Vienna Elections 2020: Analysis of parties' ads on facebook

### 2021-01-13 _post/2020-03-02-primary-schools-in-vienna/primary-schools-in-vienna.Rmd
add revised primary school post

categories:
  - Austria
  - plotly

preview: static-maps-with-mapbox-background-images-snapbox_files/preview.png

@@

# Analysis
So, triggered by this ‘hearsay’ (and, guilty as charged, by my affinity with R), I wanted to dig a bit deeper and see whether ‘the data’ has anything pertaining to say. The straightforward approach would be simply to look at the share of kids with first languages other than German in each school and compare them. While this data is certainly collected (when enrolling your kid), as far as I can tell, it is not made publicly available on an individual school level (and maybe that’s actually good). However, during our school search I came across a rather informative map provided by Austria’s statistical office (see [here]( https://www.statistik.at/atlas/schulen/#){target=”_blank”}). The map presents not only the location for every (primary) school in Austria, but also data on the school subsequently attended by its pupils once they finished the fourth grade. See e.g. <br>![Example of table of 4th graders' school destination](/post/2020-02-17-primary-schools-in-vienna_files/vienna_schools_table.PNG){width=50% height=50%}.

>>>>

categories:
  - Austria
  - plotly
  - crosstalk

preview: primary-schools-in-vienna_files/preview.png

@@

# Analysis
So, triggered by this ‘hearsay’ (and, guilty as charged, by my affinity with R), I wanted to dig a bit deeper and see whether ‘the data’ has anything pertaining to say. The straightforward approach would be simply to look at the share of kids with first languages other than German in each school and compare them. While this data is certainly collected (when enrolling your kid), as far as I can tell, it is not made publicly available on an individual school level (and maybe that’s actually good). However, during our school search I came across a rather informative map provided by Austria’s statistical office (see [here]( https://www.statistik.at/atlas/schulen/#){target=”_blank”}). The map presents not only the location for every (primary) school in Austria, but also data on the school subsequently attended by its pupils once they finished the fourth grade. See e.g. the image below. <br>

![Example of table of 4th graders' school destination](primary-schools-in-vienna_files/vienna_schools_table.PNG){width=50% height=100%}
<br>

### 2021-01-13 _post/2020-12-19-vienna-elections-2020-analysis-of-parties-ads-on-facebook/welcome.Rmd
add revised primary school post

author:
  - first_name: "Roland"
    last_name: "Schmidt"
    url: https://werk.statt.codes
    # affiliation: home 
    # affiliation_url: https://orcid.org/0000-0002-6897-1693
    orcid_id: 0000-0002-6897-1693
categories:
  - Austria
  - social media
  - election
date: 12-19-2020
preview: welcome_files/preview.png

>>>>

author:
  - first_name: "Roland"
    last_name: "Schmidt"
    url: https://werk.statt.codes
    # affiliation: home 
    # affiliation_url: https://orcid.org/0000-0002-6897-1693
    orcid_id: 0000-0002-6897-1693
categories:
  - Austria
  - social media
  - elections
date: 12-19-2020
preview: welcome_files/preview.png
